Median Maximum Pairwise Distance

### 2020-10-01 main.Rmd
commit for new branch
introduction and drake workflow

Take an example of a data set which are observed at fine temporal scales, like that of NYC bike usage available at https://www.citibikenyc.com/system-data. We use the `nyc_bikes` data set from the R package `tsibbledata` which takes a sample of 10 bikes for the year 2018. The `start_time` and the `stop_time` are recorded to a fineness of seconds. We can look at pair of cyclic granularities (hour_day, wknd_wday) or (week_month, day_week) to see how these periodicities interact. But there could be other pairs that are important too. How to understand which pairs are sufficient to explore given the data set without losing much information about the data.

When we need to understand the interplay of different periodicities in a high frequency temporal datasets, we have many choices to consider. In [@wang2019tsibble] and [@wang2020calendar], periodicities are explored across hour of the day and day of the week or months. But calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions. The paper (gravitas) describes how we can start with all possible combinations of cyclic time granularities and narrow down our search to harmonies and remove clashes without losing any perspectives about the data. Even after excluding clashes, the list of harmonies left could be large and overwhelming for human consumption. Hence, there is a need to rank the harmonies basis how well they capture the variation in the measured variable and additionally reduce the number of harmonies for further exploration/visualization. Assuming a numeric response variable, our graphics are displays of distributions compared across combinations of categorical variables, one placed at x-axis and the other on the facet. Gestalt theory suggests that when items are placed in close proximity, people assume that they are in the same group because they are close to one another and apart from other groups. Hence, displays that capture more variation within different categories in the same group would be important to bring out different patterns of the data. Here, we have two main objectives:

@@

```{r distv11}

```{r distv12}

```{r distv13}

```{r distv14}

>>>>

Take the example of the calendar display of electricity smart meter data used in @wang2020calendar for four households in Melbourne, Australia. The authors show how hour-of-the-day interact with weekday and weekends and then move on to use calendar display to display the daily schedules. The calendar display has several components in it which helps us to look at energy consumption across hour-of-the-day, day-of-the-week, week-of-the-month and month-of-the-year all at once.
Some interaction of these cyclic granularities[@our-paper] could also be interpreted from this display. However, there are two things that might be of concern. Due to the combination of linear and cyclic representation of time, it is difficult to comprehend the interaction of periodicities at once from this display. For example, this display might not be the best to understand how hour-of-the-day or month-of-year varies across week-of-the-month. Further, it is not clear what all interactions of cyclic granularities should be read from this display as there could be many combinations that one can look at. Moreover, calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions (@our-paper) and could include other cyclic granularities like hour-of-week or day-of-fortnight which could potentially become useful depending on context. Lastly, there might be certain interactions which are interesting and others which are not. It could be potentially useful to know which all cyclic granularities could be useful.

<!-- Take an example of a data set which are observed at fine temporal scales, like that of NYC bike usage available at https://www.citibikenyc.com/system-data. We use the `nyc_bikes` data set from the R package `tsibbledata` which takes a sample of 10 bikes for the year 2018. The `start_time` and the `stop_time` are recorded to a fineness of seconds. We can look at pair of cyclic granularities (hour_day, wknd_wday) or (week_month, day_week) to see how these periodicities interact. But there could be other pairs that are important too. How to understand which pairs are sufficient to explore given the data set without losing much information about the data. -->

<!-- When we need to understand the interplay of different periodicities in a high frequency temporal datasets, we have many choices to consider. In [@wang2019tsibble] and [@wang2020calendar], periodicities are explored across hour of the day and day of the week or months. But calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions. -->

The paper (gravitas) describes how we can start with all possible combinations of cyclic time granularities and narrow down our search to harmonies and remove clashes without losing any perspectives about the data. Even after excluding clashes, the list of harmonies left could be large and overwhelming for human consumption. Hence, there is a need to rank the harmonies basis how well they capture the variation in the measured variable and additionally reduce the number of harmonies for further exploration/visualization. Assuming a numeric response variable, our graphics are displays of distributions compared across combinations of categorical variables, one placed at x-axis and the other on the facet. Displays that capture more variation within different categories in the same group would be important to bring out different patterns of the data. Here, we have two main objectives:

@@

<!-- ```{r distv11} -->

<!-- ```{r distv12} -->

<!-- ```{r distv13} -->

<!-- ```{r distv14} -->
